A systematic measurement on starspot contrast from TESS and K2 bandpass differences

### 2022-07-28 papers/paper1/ms.tex
Added some more citations

@@

\begin{deluxetable}{chc}
  \tablecaption{Annotated bibliography for intro\label{table1}}
  \tablehead{
    \colhead{Reference} & \nocolhead{two} & \colhead{Key idea}
  }
  \startdata
  \citet{gullysantiago17} & - & LkCa~4 starspot spectral decomposition\\
  \citet{2015ApJ...807..174S} & - & Radius inflation from spots \\
  Strassmeier & - & Starspots review \\
  Rackham & - & TLSE \\
  \enddata
\end{deluxetable}

>>>>

% Enable for dark mode
% \usepackage{xcolor}
% \pagecolor{black}
% \color{white}

@@

\begin{deluxetable}{chc}
  \tablecaption{Annotated bibliography for intro\label{table1}}
  \tablehead{
    \colhead{Reference} & \nocolhead{two} & \colhead{Key idea}
  }
  \startdata
  \citet{gullysantiago17} & - & LkCa~4 starspot spectral decomposition\\
  \citet{2015ApJ...807..174S} & - & Radius inflation from spots \\
  Strassmeier & - & Starspots review \\
  \citet{2018ApJ...853..122R} & - & TLSE \\
  \citet{Kochukhov21} & - & Magnetic fields of M dwarfs \\
  \citet{2021sf2a.conf..363B} & - & Stellar rotation using ROOSTER \\
  \citet{2015MNRAS.450.3211A} & - & Using Kepler to study stellar rotation \\
  \citet{2022ApJ...927..219C} & - & Using deep learning to recover TESS light curves \\
  \citet{2021AJ....162..123L} & - & Test Lightcurve and study stellar surfaces \\
  \citet{2022ApJ...925..185D} & - & Lightcurves for oblate, rapid rotators \\
  \citet{Reinhold2013} & - & Measure rotation of active Kepler Stars \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\  
  \enddata
\end{deluxetable}
